---
title: "Ravia Datasets"
author: "Robert Pellegrino"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  word_document: default
  html_document: default
note: 1st exploratory analysis
---

## Loadoad Packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = FALSE,warning = FALSE)

R.Version()$version.string #code ran on R version 4.0.3 (2020-10-10)

# Load packages
pacman::p_load(tidyverse)
               
```

# Data Processing
## Process Datasets
Ravia et al. 2021 experiments are broken into four components:
* Similarity Ratings
** Includes the mixture number that are being compared as well as their similarity rating
* Mixtures
** List the mixtures (lookup number) and their respective component odorants
* Intensity
** List individual odorants and their intensity
* Discrimination
** List discrimination ability between two mixtures

Experiment breakdown:
* Experiment 1
** Similarity rating between several mixtures varying in intensity
* Experiment 2
** Similarity rating between several mixtures varying in intensity
* Experiment 3 - Similarity ratings not included in Supplementary
** Bell challenge: similarity rating between three mixtures by perfumer
* Experiment 4  
** 50 pairs of mixture discriminated with triangle test by 27 subjects in replicate. 100 trials/subject
* Experiment 5  
** 50 pairs of mixtures discriminated with two-alternative same–different task by 30 subjects in replicate. Each odorant was used at two different concentration. 400 trials/subject
* Experiment 6  
** 40 pairs of mixtures discriminated with two-alternative same–different task by 25 subjects in replicate. Each odorant was used at two different concentration. 320 trials/subject
* Experiment 7 - Excluded from this analysis
** Metemors discrimination on individual level

```{r}
# Set file path for Joel if it exists
  if (dir.exists("/Users/jmainland/Dropbox (Mainland Lab)/Mainland Lab Team Folder/Bob/snitz")){
  path="/Users/jmainland/Dropbox (Mainland Lab)/Mainland Lab Team Folder/Bob/ravia"
}else path=".."

# Read in Ravia Experiments and manipulate for combining
  ## Odorants     
     db.ravia.lookup <- read.csv(paste0(path,"/Data/Raw/tableS1.csv")) %>%
       filter(Type != "mono-molecule", Experiment != "Exp7") %>%
       na_if(0) %>%
       unite("Mixture.Cids", starts_with("Mix.Component"), na.rm = TRUE, remove = FALSE, sep = " ") %>%
       select(ID.In.Exp.1, Mixture.Cids, Experiment) %>%
       rename(Mixture.number = ID.In.Exp.1)
     
  ## Intensity
     db.ravia.intensity <- read.csv(paste0(path,"/Data/Raw/tableS1.csv")) %>%
       filter(Type == "mono-molecule", Experiment != "Exp7") %>%
       select(CID, Dilution1, Intensity1, Dilution2, Intensity2, Dilution3, Intensity3, Experiment) %>%
       na_if("Blank")
     
  ## Similarity
     db.ravia.similar <- read.csv(paste0(path,"/Data/Raw/tableS2.csv")) %>%
       rename(Comparison.number = Number, Mixture.number = Mixture1Id,  Mixture.number.1 = Mixture2Id, Average.rated.similarity = RatedSimilarity) %>%
       select(Comparison.number, Mixture.number, Mixture.number.1, Average.rated.similarity, Experiment)
       
  ## Discrimination   
     db.ravia.discrim <- read.csv(paste0(path,"/Data/Raw/tableS3.csv")) %>%
       filter(Experiment != "Exp7") %>%
       select(-c(Mixture3, Mixture4)) %>%
       rename(Comparison.number = CompareIndex, Mixture.number = Mixture1,  Mixture.number.1 = Mixture2)
     
# Save processed data to RDS
  saveRDS(db.ravia.similar, file = paste0(path,"/Data/Processed/db.ravia.similar.rds"))
  saveRDS(db.ravia.lookup, file = paste0(path,"/Data/Processed/db.ravia.lookup.rds"))
  saveRDS(db.ravia.intensity, file = paste0(path,"/Data/Processed/db.ravia.intensity.rds"))
  saveRDS(db.ravia.discrim, file = paste0(path,"/Data/Processed/db.ravia.discrim.rds"))
    
# Save processed data to csv
  write.csv(db.ravia.similar, file = paste0(path,"/Data/Processed/ravia_2021/behavior1.csv"), row.names = FALSE)
  write.csv(db.ravia.lookup, file = paste0(path,"/Data/Processed/ravia_2021/mixtures.csv"), row.names = FALSE)
  write.csv(db.ravia.intensity, file = paste0(path,"/Data/Processed/ravia_2021/intensity.csv"), row.names = FALSE)
  write.csv(db.ravia.discrim, file = paste0(path,"/Data/Processed/ravia_2021/behavior2.csv"), row.names = FALSE)
    
```

